Enforced Invariant Confluence

### 2018-02-23 doc/paper_redux/iconfluence.tex
Minor tweaks.

\subsubsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph where
vertices are states, and edges are either labelled with transactions or are
unlabelled if they correspond to a join. The graph is really just an alternate
way of representing an execution in the process-based model, but with duplicate
states collapsed into a single vertex. As with the process-based model, we say
that $T$ is \Iconfluent{} if every vertex in the graph satisfies the invariant.

@@

Bailis et al.\ defined \Iconfluence{} to mean that expressions recursively
satisfying $I$ are closed under join. That is, $T$ is \Iconfluent{} if
\[
  \forall e_1, e_2.\; \Irec{e_1} \land \Irec{e_2} \implies I{e_1 \join e_2}
\]
If $\lnot I(s_0)$, then \Iconfluence holds vacuously which is a bit silly, so
Bailis et al.\ probably ought to have also added the condition $I(s_0)$ to
their definition of \Iconfluence{}. Doing so, the two definitions become
equivalent.

@@

    \item
      $I(s_0)$ and $\Irec{e_1} \land \Irec{e_2} \implies I{e_1 \join e_2}$
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). Axiomatically, $\reachable{s_0}$, so by
  (1), $I(s_0)$. Let $e_1$ and $e_2$ be arbitrary expressions such that
  $\Irec{e_1}$ and $\Irec{e_2}$. By \clmref{state_irec_implies_reachable},
  $\reachable{e_1}$ and $\reachable{e_2}$. Thus, $\reachable{e_1 \join e_2}$,
  so by (1), $I(e_1 \join e_2)$.

@@

\subsubsection{Graph-Based}
In the graph-based model, we are given a directed acyclic graph in which each
vertex is a state $s$ and each edge is labelled with a shadow operation $t(s)$
where $s$ is some other vertex in the graph. $T$ is \Iconfluent{} if every
vertex in the graph satisfies $I$.

@@

    \item \textbf{Case $t(e_1)(e_2)$.}
      $\Irec{t(e_1)(e_2)}$, so $\Irec{e_1}$, $\Irec{e_2}$, and $t(e_1)(e_1)$.
      By the inductive hypothesis, $\reachable{e_1}$ and $\reachable{e_2}$.
      Thus, $\reachable{t(e_1)(e_2)}$.
  \end{itemize}
\end{elidableproof}

@@

  Next, we show that (2) implies (1). We show by structural induction that
  $\reachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      By (2), $I(s_0)$, so $\Irec{s_0}$.

>>>>

\subsubsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph where
vertices are states, and edges are either labelled with transactions or are
unlabelled if they correspond to a join. The graph is really just an alternate
way of representing an execution in the process-based model, but with duplicate
states collapsed into a single vertex. As with the process-based model, we say
that $T$ is \Iconfluent{} if every vertex in every graph satisfies the
invariant.

@@

Bailis et al.\ defined \Iconfluence{} to mean that expressions recursively
satisfying $I$ are closed under join. That is, $T$ is \Iconfluent{} if
\[
  \forall e_1, e_2.\; \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)
\]
If $\lnot I(s_0)$, then \Iconfluence{} holds vacuously which is a bit silly, so
Bailis et al.\ probably ought to have also added the condition $I(s_0)$ to
their definition of \Iconfluence{}. Doing so, the two definitions become
equivalent.

@@

    \item
      $I(s_0)$ and $\Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)$
  \end{enumerate}
\end{claim}
\begin{elidableproof}
  First, we show that (1) implies (2). Axiomatically, $\reachable{s_0}$, so by
  (1), $I(s_0)$. Let $e_1$ and $e_2$ be arbitrary expressions such that
  $\Irec{e_1}$ and $\Irec{e_2}$. By \clmref{state_irec_implies_reachable},
  $\reachable{e_1}$ and $\reachable{e_2}$. Thus, $\reachable{e_1 \join e_2}$,
  so by (1), $I(e_1 \join e_2)$.

@@

\subsubsection{Graph-Based}
In the graph-based model, we are given a directed acyclic graph in which each
vertex is a state $s$ and each edge is labelled with a shadow operation $t(s)$
where $s$ is some other vertex in the graph. $T$ is \Iconfluent{} if every
vertex in every graph satisfies $I$.

@@

    \item \textbf{Case $t(e_1)(e_2)$.}
      $\Irec{t(e_1)(e_2)}$, so $\Irec{e_1}$, $\Irec{e_2}$, and
      $I(t(e_1)(e_1))$. By the inductive hypothesis, $\reachable{e_1}$ and
      $\reachable{e_2}$. Thus, $\reachable{t(e_1)(e_2)}$.
  \end{itemize}
\end{elidableproof}

@@

  Next, we show that (2) implies (1). We show by structural induction on $e$
  that $\reachable{e} \implies \Irec{e}$. From this, (1) is immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      By (2), $I(s_0)$, so $\Irec{s_0}$.
